Gut microbes and their genes are associated with cognition and neuroanatomy in children

### 2023-03-28 manuscript/main.tex
added "weighted" and corrected numbers
Changed text to reflect the proportion before filtering by improtant taxa

While models for many regions were highly concordant across the
left and right hemispheres in terms of both model performance and
microbial feature importance, other regions had substantial
bilateral differences. For example, the left accumbens area
has one of the highest test-set correlations of our
brain region models (R = 0.288), as compared to the right which
had a negative mean test-set correlation (R = -0.041),
indicating that generalizable models were not identified.
Feature importance for models of the left accumbens area were dominated
by three species of \emph{Bacteroides}: \emph{B. vulgatus} (3.4\%
relative importance), \emph{B. ovatus} (3.7\% relative importance), and
\emph{B. uniformis} (3.0\% relative importance).

While RF models for multiple brain regions had many important microbial taxa,
others were dominated by a small number of taxa, many of which
were also identified in LMs and RF models of cognitive function (Figures 2 and 3). 
In general, for all segments, a
consistent number of species between 14 and 22 (median = 20) was
responsible for one third of the fitness-weighted cumulative importance,
regardless of model performance (Figure 4A-B, Table S2).
We observed two major patterns of importance distribution from
species over the brain segments; some species portrayed high contributions
to multiple different segments, while others contributed modestly to
just one or two brain segments. Notable cases of the first pattern
included seven species - \emph{Anaerostipes hadrus}, \emph{Bacteroides
vulgatus}, \emph{Fusicatenibacter saccharivorans}, \emph{Ruminococcus
torques}, \emph{Eubacterium rectale}, \emph{Coprococcus comes} and
\emph{Blautia wexlerae} - that combined, account for approximately one
third of the cumulative relative importances, computed after subsetting
on the taxa of interest (Figure 4C).

>>>>

While models for many regions were highly concordant across the
left and right hemispheres in terms of both model performance and
microbial feature importance, other regions had substantial
bilateral differences. For example, the left accumbens area
has one of the highest test-set correlations of our
brain region models (R = 0.288), as compared to the right which
had a negative mean test-set correlation (R = -0.041),
indicating that generalizable models were not identified.
Feature importance for models of the left accumbens area were dominated
by three species of \emph{Bacteroides}: \emph{B. vulgatus} (3.3\%
relative weighted importance), \emph{B. ovatus} (3.7\% relative weighted importance), and
\emph{B. uniformis} (2.9\% relative weighted importance).

While RF models for multiple brain regions had many important microbial taxa,
others were dominated by a small number of taxa, many of which
were also identified in LMs and RF models of cognitive function (Figures 2 and 3). 
In general, for all segments, a consistent number of species between 31 and 45 (median = 37, less than 30\% of the input features)
was responsible for half of the fitness-weighted cumulative importance,
regardless of model performance (Figure 4A-B, Table S2).
We observed two major patterns of importance distribution from
species over the brain segments; some species portrayed high contributions
to multiple different segments, while others contributed modestly to
just one or two brain segments. Notable cases of the first pattern
included seven species - \emph{Anaerostipes hadrus}, \emph{Bacteroides
vulgatus}, \emph{Fusicatenibacter saccharivorans}, \emph{Ruminococcus
torques}, \emph{Eubacterium rectale}, \emph{Coprococcus comes} and
\emph{Blautia wexlerae} - that combined, account for approximately one
third of the cumulative relative importances, computed after subsetting
on the taxa of interest (Figure 4C).
